site_map

### 2020-01-17 site_map.Rmd
update

library(tidyverse)
library(plyr)
library(lubridate)
library(ggpubr)
library(zoo)
library(lubridate)
library(FNN)
library(forecast)
library(astrochron)
library(WaveletComp)
library(data.table)
library(heatwaveR)
library(viridis)
library(ggrepel)
library(plyr)
library(maptools)
library(sp)
library(geosphere)
library(PBSmapping)
library(scales)
library(grid)
library(gridExtra)
library(circular)
library(fossil)
library(mapproj)
library(ncdf4)
library(reshape2)
library(plyr) # Never load plyr when also loading the tidyverse. It causes a lot of conflicts.
library(stringr)
library(doMC); doMC::registerDoMC(cores = 4)
library(fasttime)
library(xtable)
library(ggpubr)
library(ggpubr); theme_set(theme_pubr())# library(devtools)
install_github("marchtaylor/sinkr")

@@

# Pixel points
site_pixels <- data.frame()
for(i in 1:length(west$site)){
  site <- site_transects[i,]
  site_pixel <- transect.pixel(site, c(10000, 20000, 30000, 40000, 50000)) # RWS: fixed error
  site_pixels <- rbind(site_pixels, site_pixel)
}

# save(site_pixels, file = "Data/site_pixels.RData")
load("Data/site_pixels.RData")

@@

load("Data/south_africa_coast.RData")
load("Data/africa_coast.RData")
load("Data/sa_provinces_new.RData")
load("Data/site_list_sub.Rdata")
load("Data/site_pixels.RData")
load("MUR.RData")
names(south_africa_coast)[1] <- "lon"

@@

@@

site
site_map

pdf("Figures/site_map.pdf", width = 10, height = 7, pointsize = 4) # Set PDF dimensions

africa_map <- ggplot(africa_coast, aes(x = lon, y = lat)) + 
  theme_bw() + 
  coord_equal() + 
  geom_polygon(aes(group = group), colour = "black", fill = "grey80") + 
  geom_polygon(data = sa_provinces_new, (aes(group = group))) +
  annotate("text", label = "Africa", x = 16.0, y = 15.0, size = 3) + 
  theme(panel.border = element_rect(colour = "black", size = 0.4), 
        plot.background = element_blank(), 
        axis.ticks = element_blank(), 
        axis.text = element_blank(), 
        axis.title = element_blank(), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  coord_map(xlim = c(-20, 53), ylim = c(-36, 38), projection = "mercator") 
africa_map

# More mapping - http://r-nold.blogspot.com/2014/06/creating-inset-map-with-ggplot2.html

vp1 <- viewport(x = 0.70, y = 0.58, w = 0.25, h = 0.25) # Africa
vp2 <- viewport(x = 1.0, y = 1.0, w = 1.00, h = 1.00, just = c("right", "top"))  # South Africa
print(site_map, vp = vp2)
print(africa_map, vp = vp1)
dev.off()
pdf("Figures/map_fixed.pdf", width = 10, height = 7, pointsize = 4) # Set PDF dimensions
```

>>>>

library(tidyverse)
library(plyr)
library(lubridate)
library(ggpubr)
library(zoo)
library(lubridate)
library(FNN)
library(forecast)
library(astrochron)
library(WaveletComp)
library(data.table)
library(heatwaveR)
library(viridis)
library(ggrepel)
library(plyr)
library(maptools)
library(sp)
library(geosphere)
library(PBSmapping)
library(scales)
library(grid)
library(gridExtra)
library(circular)
library(fossil)
library(mapproj)
library(ncdf4)
library(reshape2)
library(plyr) # Never load plyr when also loading the tidyverse. It causes a lot of conflicts.
library(stringr)
library(doMC); doMC::registerDoMC(cores = 4)
library(fasttime)
library(xtable)
library(ggpubr)
library(ggpubr); theme_set(theme_pubr())# library(devtools)
# install_github("marchtaylor/sinkr")

@@

# Pixel points
site_pixels <- data.frame()
for(i in 1:length(west$site)){
  site <- site_transects[i,]
  # site_pixel <- transect.pixel(site, c(10000, 20000, 30000, 40000, 50000)) # RWS: fixed error
  site_pixel <- transect.pixel(site, c(10000, 30000, 50000))
  site_pixels <- rbind(site_pixels, site_pixel)
}

# New site pixels
save(site_pixels, file = "Data/site_pixels_new.RData")
load("Data/site_pixels_new.RData")
# save(site_pixels, file = "Data/site_pixels.RData")
# load("Data/site_pixels.RData")

@@

load("Data/south_africa_coast.RData")
load("Data/africa_coast.RData")
load("Data/sa_provinces_new.RData")
load("Data/site_list_sub.Rdata")
load("Data/site_pixels_new.RData")
# load("Data/site_pixels.RData")
load("MUR.RData")
names(south_africa_coast)[1] <- "lon"

@@

site_list_sub_map <- site_list_sub %>% 
  select(site,lat,lon)

@@

site_map <- ggplot(data = south_africa_coast, aes(x = lon, y = lat)) + bw_update +
  # geom_raster(data = MUR, aes(x = lon, y = lat, fill = temp)) +
   geom_polygon(data = south_africa_coast, aes(x = lon, y = lat, group = group),
                fill = "grey", colour = "grey", size = 0.1, show.legend = FALSE) +
  geom_point(data = site_list_sub, aes(x = lon, y = lat), alpha = 0.8, size = 5) +
  geom_point(data = site_pixels, aes(x = lon, y = lat), colour = "white", shape = 0, alpha = 0.8, size = 2.1) +
  geom_label_repel(data =site_list_sub_map, aes(x = lon, y = lat, label = site), 
                     size = 4, box.padding = 2, nudge_x = -0.5, nudge_y = 0.2, 
                     segment.alpha = 0.4, force = 0.1) +
  coord_equal(xlim = c(12, 23), ylim = c(-36,-26), expand = 0) +
  # geom_rect(data = bbox, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
  #           alpha = 0.4, colour = "red", size = 0.1, linetype = 1) +
  # scale_x_continuous(limits = sa_lons, expand = c(0, 0), breaks = seq(15, 35, 5)) +
  # scale_y_continuous(limits = sa_lats, expand = c(0, 0), breaks = seq(-35, -30, 5)) +
  scale_fill_viridis(
    option = "magma",
    name = "Temperature (°C)",
    alpha = 0.8) +
  xlab("") + ylab("") +
  # annotate("text", label = "INDIAN\nOCEAN", x = 32.00, y = -35.0,
  #            size = 4, angle = 0, colour = "black") +
    annotate("text", label = "ATLANTIC\nOCEAN", x = 17.00, y = -35.0,
             size =6, angle = 0, colour = "black") +
    annotate("text", label = "Benguela", x = 14.0, y = -29.5,
             size = 6, angle = 302, colour = "black") +
    # annotate("text", label = "Agulhas", x = 31.7, y = -31.7,
    #          size = 5, angle = 50, colour = "black") +
  guides(fill = guide_colourbar()) +
  scale_x_continuous(expand = c(0, 0),
                       labels = scales::unit_format(unit = "°E", sep = "")) +
    scale_y_continuous(expand = c(0, 0),
                       labels = scales::unit_format(unit = "°S", sep = "")) +
  theme(panel.background = element_rect(fill = "ivory", colour = NA),
        panel.border = element_rect(colour = "black", size = 0.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.key = element_blank(),
        legend.background = element_blank(),
        axis.ticks = element_line(size = 0.5),
        axis.text = element_text(size = 12)) +
    guides(fill = guide_colourbar(barheight = 1.00, barwidth = 10)) +
  theme(panel.background = element_rect(fill = "ivory", colour = NA),
        panel.border = element_rect(colour = "black", size = 0.5),
        panel.grid.minor = element_line(colour = "NA"),
        panel.grid.major = element_line(colour = "ivory", size = 0.2, linetype = "dotted"),
        legend.direction = "horizontal",
        legend.justification = c(1,0),
        legend.position = c(0.85, 0.70),
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 8),
        legend.key = element_blank(),
        legend.background = element_blank(),
        axis.ticks = element_line(size = 0.5))
site_map

# pdf("Figures/site_map.pdf", width = 10, height = 7, pointsize = 4) # Set PDF dimensions
# 
# 
# africa_map <- ggplot(africa_coast, aes(x = lon, y = lat)) + 
#   theme_bw() + 
#   coord_equal() + 
#   geom_polygon(aes(group = group), colour = "black", fill = "grey80") + 
#   geom_polygon(data = sa_provinces_new, (aes(group = group))) +
#   annotate("text", label = "Africa", x = 16.0, y = 15.0, size = 3) + 
#   theme(panel.border = element_rect(colour = "black", size = 0.4), 
#         plot.background = element_blank(), 
#         axis.ticks = element_blank(), 
#         axis.text = element_blank(), 
#         axis.title = element_blank(), 
#         panel.grid.major = element_blank(), 
#         panel.grid.minor = element_blank()) +
#   coord_map(xlim = c(-20, 53), ylim = c(-36, 38), projection = "mercator") 
# africa_map
# 
# # More mapping - http://r-nold.blogspot.com/2014/06/creating-inset-map-with-ggplot2.html
# 
# vp1 <- viewport(x = 0.70, y = 0.58, w = 0.25, h = 0.25) # Africa
# vp2 <- viewport(x = 1.0, y = 1.0, w = 1.00, h = 1.00, just = c("right", "top"))  # South Africa
# print(site_map, vp = vp2)
# print(africa_map, vp = vp1)
# dev.off()
# pdf("Figures/map_fixed.pdf", width = 10, height = 7, pointsize = 4) # Set PDF dimensions
```

# SIte map 2

```{r}

site_list_sub_map <- site_list_sub %>% 
  select(site,lat,lon)

mapping_plot <- function(df, xy = "salmon"){
  mapping <- df %>% 
    ggplot(aes(x = lon, y = lat)) +
    geom_polygon(data = south_africa_coast, aes(group = group), fill = "white") +
    coord_cartesian(xlim = c(12, 36), ylim = c(-32, -20)) +
    geom_path(data = sa_provinces_new, aes(group = group)) +
    geom_point(data = df, colour = xy, size = 4)  +
    geom_label_repel(data =df, aes(x = lon, y = lat, label = site), 
                     size = 6, box.padding = 2, nudge_x = -0.5, nudge_y = 0.2, 
                     segment.alpha = 0.4, force = 0.1) +
    coord_equal(xlim = c(15, 35), ylim = c(-37, -27)) +
    annotate("text", label = "INDIAN\nOCEAN", x = 35.00, y = -34.0, size = 6.0, angle = 0, colour = "black") +
    annotate("text", label = "ATLANTIC\nOCEAN", x = 16.00, y = -37.0, size = 6.0, angle = 0, colour = "black") +
    # geom_segment(aes(x = 17.2, y = -32.6, xend = 15.2, yend = -29.5),
    #               arrow = arrow(length = unit(0.3, "cm")), size = 0.1, colour = "black") +
    #   annotate("text", label = "Benguela", x = 14.0, y = -31.8, size = 3.5, angle = 298, colour = "black") +
    #   geom_segment(aes(x = 33, y = -29.5, xend = 29.8, yend = -33.0),
    #               arrow = arrow(length = unit(0.3, "cm")), size = 0.1, colour = "black") +
    annotate("text", label = "Agulhas", x = 31.7, y = -31.7, size = 7.5, angle = 53, colour = "black") +
    scale_x_continuous(labels = scales::unit_format(unit = "°E", sep = "")) +
    scale_y_continuous(labels = scales::unit_format(unit = "°S", sep = "")) +
    labs(x = NULL, y = NULL) +
    coord_cartesian(xlim = c(10.5, 39.5), ylim = c(-39.5, -25.5), expand = F) +
    scaleBar(lon = 32.0, lat = -38.7, distanceLon = 200, distanceLat = 50, 
             distanceLegend = 90, dist.unit = "km", arrow.length = 100,
             arrow.distance = 130, arrow.North.size = 3) +  
    coord_equal() +
    theme(aspect.ratio = 1)  +
    theme_bw() +
    theme(panel.border = element_rect(fill = NA, colour = "black", size = 1),
          axis.text = element_text(colour = "black", size = 22),
          axis.title = element_text(colour = "black", size = 22))
  return(mapping)
}

Map <- mapping_plot(df = site_list_sub_map, xy = "salmon")

```
